Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-16 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-16 16-55-28

As addressed in section~\ref{sec:introduction}, Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays.
The method utilizes information of MPPs of every PV panel that is extracted using an online monitoring\cite{Carotenuto2014} and a power estimation\cite{Orozco-Gutierrez2015}.
Firstly, PV panel characteristics (current values, voltage values) are extracted and closed values are grouped.

\section{Feasibility Problem}\label{sec:feasibility-problem}
\subsection{Problem setting}\label{sec:problem-setting}
\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

>>>>

As addressed in section~\ref{sec:introduction}, Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays.
The method utilizes information of MPPs of every PV panel that is extracted using an online monitoring\cite{Carotenuto2014} and a power estimation\cite{Orozco-Gutierrez2015}.

Firstly, maximum power points of PV panels are extracted by using online monitoring from\cite{Carotenuto2014}.
Then the current and voltage levels of maximum power point for each PV module $s$, $I_{mpp_{s}}$and $V_{mpp_{s}}$, are estimated from maximum power points of PV panels using the method in\cite{Orozco-Gutierrez2015}.

Estimated maximum power point current values ($I_{mpp_s}$) are approximated and close values are grouped into a small number of classes so that the number of possible combinations, in other words, search space is reduced.
Estimated maximum power point voltage values ($V_{mpp_s}$) are averaged and the mean value $\Bar{V}_{mpp}$ of all PV modules is used to approximate MPP voltage in the string.
MPP voltage is approximated by $m \times \Bar{V}_{mpp} $ where $m$ is the number of active modules at the MPP.
Then possible combination of configurations are enumerated.

For furthermore power simulation and configuration implementation, the current sequence and number of activating PV modules pre-string (it is called $feasibility$) are examined for each configuration.
A simple feasibility checking method provided in \cite{Orozco-Gutierrez2016} are described as follow.

\textbf{(Feasibility 1)}\footnote{In \cite{Orozco-Gutierrez2016}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }
For each $n$-th highest current level $I_{n}$ in a current sequence for strings,
it is required that the number of active modules in a configuration is $N(I_{n}) / n$ or less, where $N(I)$ is the total number of active modules for a current level $I$. 
The maximum number $M$ of active modules for a PV array is given as
\begin{equation}
    M=\mbox{min}\begin{Bmatrix}
N(I),\frac{N(I_2)}{2},\frac{N(I_3)}{3},\cdots,\frac{N(I_{n})}{n}
\end{Bmatrix}.
\label{eq:1}
\end{equation}
Thus, approximated power $P$ can be calculated as follow.
\begin{equation}
\label{eq:2}
P=\sum{I_{n}}\times M \times \Bar{V}_{mpp}
\end{equation}

Approximated power values with and only with \textbf{Feasibility 1} is satisfied are listed into a power matrix like Table~\ref{tab:power-matrix}.
The configuration with  maximum power value and configurations whose powers are more than 77\% of maximum power are selected as configuration candidates\cite{Orozco-Gutierrez2016}.

\section{Feasibility}
From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}

\begin{table*}[t]
  \caption{}
  \centerline{APPROXIMATED POWER}
  \vskip5pt
\label{tab:power-matrix}
\centering
\begin{tabular}{c|rrrrrrrrrrr}
\hline\hline	
\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
\end{tabular}
\end{table*}
\section{Algorithm to identify feasibility}\label{sec:algor-ident-feas}
\subsection{Feasibility problem}\label{sec:feasibility-problem}
\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
